Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-10-28 WSSSPE3/report/wg_appendix_software_credit.tex
Minor changes to SC appendix in response to Dan notes

At a minimum, the metadata needed for software citation (aside from the DOI for the software itself) includes:
\begin{itemize}
    \item Contributors, in the form of name and ORCID,
    \item Software dependencies, in the form of DOI, and
    \item Other people and artifacts that would be cited or acknowledged in a paper.
\end{itemize}
\katznote{is a name/title also needed?}
This information would then be contained in a citation file, e.g.,  as part of 
the GitHub repository.
The group also discussed similar efforts such as Codemeta\footnote{Codemeta: \url{https://github.com/codemeta/codemeta}}, an attempt to codify minimal 
metadata schemes in JSON and XML for scientific software and code, and 
implementing transitive credit via JSON-LD~\cite{wssspe2_katz}.
Some questions arose about how this information would be stored for 
closed-source software.

@@

Major obstacles include the fact that indexers (e.g., Scopus, Web of Science, 
Google Scholar) do not currently support software/data document types or 
DataCite DOIs.
Therefore, even with universal association of scientific software with DOIs 
and standardizing practices for citing software in publications \katznote{this sentence is missing its ed}

Although this working group's discussions at WSSSPE3 did not focus much on the 
topic of tenure, the group recognized that there is no standard policy---even 
within a single university---for software products to be included in 
promotion and tenure dossiers.
Thus, it may be difficult to encourage valuing software contributions across 
the United States or United Kingdom and globally; furthermore, stakeholders 
are typically not tenured and thus may not be influential enough. \katznote{to do what?}

>>>>

At a minimum, the metadata needed for software citation (aside from the DOI for the software itself) includes:
\begin{itemize}
    \item Name of software and DOI,
    \item Contributors, in the form of name and ORCID,
    \item Software dependencies, in the form of DOI, and
    \item Other people and artifacts that would be cited or acknowledged in a paper.
\end{itemize}
This information would then be contained in a citation file, e.g.,  as part of 
the GitHub repository.
The group also discussed similar efforts such as Codemeta\footnote{Codemeta: \url{https://github.com/codemeta/codemeta}}, an attempt to codify minimal 
metadata schemes in JSON and XML for scientific software and code, and 
implementing transitive credit via JSON-LD~\cite{wssspe2_katz}.
Some questions arose about how this information would be stored for 
closed-source software.

@@

Major obstacles include the fact that indexers (e.g., Scopus, Web of Science,  Google Scholar) do not currently support software/data document types or  DataCite DOIs.
Therefore, even with universal association of scientific software with DOIs  and standardizing practices for citing software in publications, software citations will not be indexed in the same manner as traditional publications.

Although this working group's discussions at WSSSPE3 did not focus much on the topic of tenure, the group recognized that there is no standard policy---even within a single university---for software products to be included in promotion and tenure dossiers.
Thus, it may be difficult to encourage valuing software contributions across the United States or United Kingdom and globally; furthermore, stakeholders are typically not tenured and thus may not be influential enough to change the status quo.
